\begin{thebibliography}{100}

\bibitem[B]{external}
{\bf Resulting from External Collaborations}\\ \\


\bibitem{EidhammerIet00}
I.~Eidhammer, I.~Jonassen, and W.~R. Taylor.
\newblock Structure comparison and structure patterns.
\newblock {\em J. Compu. Biol.}, 7:658--716, 2000.

\bibitem{HigginsDGet00a}
D.~G. Higgins and W.~R. Taylor.
\newblock Preface.
\newblock In D.~Higgins and W.~Taylor, editors, {\em Bioinformatics: Sequence
  structure and databases}, pages v--ix. Oxford University Press, 2000.

\bibitem{JonassenIet00a}
I.~Jonassen, I.~Eidhammer, S.~H. Grindhaug, and W.~R. Taylor.
\newblock Searching the protein structure databank with weak sequence patterns
  and structural constraints.
\newblock {\em J. Molec. Biol.}, 304:599--619, 2000.

\bibitem{HigginsDGet00b}
D.~G. Higgins and W.~R. Taylor.
\newblock Multiple sequence alignment.
\newblock In D.~M. Webster, editor, {\em Protein structure prediction}, volume
  143 of {\em Methods in Molecular Biology (ed. J.~M.~Walker)}, pages 1--18.
  Humana Press, Totowa, New Jersey, USA, 2000.

\bibitem{JonassenIet02}
I.~Jonassen, I.~Eidhammer, D.~Conklin, and W.~R. Taylor.
\newblock Structure motif discovery and mining the {PDB}.
\newblock {\em Bioinformatics}, 18:362--367, 2002.

\bibitem{ConklinDet02}
D.~Conklin, I.~Jonassen, R.~Aasland, and W.~R. Taylor.
\newblock Association of nucleotide patterns with gene function classes:
  application to human 3' untranslated sequences.
\newblock {\em Bioinformatics}, 18:182--189, 2002.

\bibitem{TaylorWRet02a}
W.~R. Taylor, J.~Heringa, F.~Baud, and T.~P. Flores.
\newblock A {Fourier} analysis of symmetry in protein structure.
\newblock {\em Protein Eng.}, 15:79--89, 2002.

K.~Petersen and W.~R. Taylor.
\newblock Modelling zinc-binding proteins with {GADGET}: Genetic algorithm and
  distance geometry for exploring topology.
\newblock {\em J. Molec. Biol.}, 325:1039--1059, 2003.

\bibitem{MombelliEet03a}
E.~Mombelli, R.~Morris, W.~R. Taylor, and F.~Fraternali.
\newblock Hydrogen-bonding propensities of sphingomyelin in solution and in a
  bilayer assembly: a molecular dynamics study.
\newblock {\em Biophys. J.}, 84:1507--1517, 2003.

\bibitem{TaylorWRet03c}
W.~R. Taylor, R.~E.~J. Munro, K.~Petersen, and R.~P. Bywater.
\newblock {\em Ab initio} modelling of the {N}-terminal domain of the secretin
  receptors.
\newblock {\em Comp. Biol. Chem.}, 27:103--114, 2003.

\bibitem{EidhammerIet04}
I.~Eidhammer, I.~Jonassen, and W.~R. Taylor.
\newblock {\em Protein Bioinformatics: an algorithmic approach to sequence and
  structure analysis}.
\newblock J. Wiley, London, 2004.

\bibitem{JohannissenLOet04}
L.~O. Johannissen and W.~R. Taylor.
\newblock Protein fold comparison by the alignment of topological strings.
\newblock {\em Prot. Engng.}, 16:949--955, 2004.

\bibitem{TaylorWRet04a}
W.~R. Taylor and I.~Jonassen.
\newblock Discovery of local packing motifs in protein structures.
\newblock {\em Proteins: struc. funct. gene.}, 34:206--219, 2004.

\bibitem{TaylorWRet05a}
W.~R. Taylor and A.~Asz\'odi.
\newblock {\em Protein Geometry, Classification, Topology and Symmetry}.
\newblock Institute of Physics, 2005.


\end{thebibliography}
