\begin{thebibliography}{100}

\bibitem[A]{internal}
{\bf Resulting from Internal Collaborations}\\ \\

\bibitem{OgunMet01}
M.~Ogun, M.~Grainger, W.~R. Taylor, and A.~A. Holder.
\newblock The merozoite surface protein-6 gene codes for a 36 {kDa}-protein
  associated with the {\em plasmodium falciparum} merozoite surface protein-1
  complex.
\newblock {\em Mol. Biochem. Parasitology}, 112:91--101, 2001.

\bibitem{TaylorWRet01b}
W.~R. Taylor, A.~C.~W. May, N.~P. Brown, and A.~Asz\'odi.
\newblock Protein structure: Geometry, topology and classification.
\newblock {\em Rep. Prog. Phys.}, 64:517--590, 2001.

\bibitem{TaylorWRet02a}
W.~R. Taylor, J.~Heringa, F.~Baud, and T.~P. Flores.
\newblock A {Fourier} analysis of symmetry in protein structure.
\newblock {\em Protein Eng.}, 15:79--89, 2002.

\bibitem{SaldanhaJWet02a}
J.~W. Saldanha, P.~E. Czabotar, A.~J. Hay, and W.~R. Taylor.
\newblock A model for the cytoplasmic domain of the influenza {A} virus {M2}
  channel by analogy to the {HIV-1 Vpu} protein.
\newblock {\em Protein Peptide Letts.}, 9:495--502, 2002.

\bibitem{LinKet02a}
K.~Lin, A.~C. May, and W.~R. Taylor.
\newblock Amino acid substitution matrices from an artificial neural network
  model.
\newblock {\em J. Comput Biol.}, 8:471--481, 2002.

\bibitem{LinKet02b}
K.~Lin, A.~C. May, and W.~R. Taylor.
\newblock Threading using neural networks ({TUNE}): the measure of protein
  sequence-structure compatibility.
\newblock {\em Bioinformatics}, 18:1350--1357, 2002.

\bibitem{LinKet02c}
K.~Lin, A.~C. May, and W.~R. Taylor.
\newblock Amino acid encoding schemes from protein structural alignments:
  multidimensional vectors to describe residue types.
\newblock {\em J. Theor. Biol.}, 221:361--365, 2002.

\bibitem{LinKet03a}
K.~Lin, W.~R. Taylor, J.~Klienjung, and J.~Heringa.
\newblock {CAO} matrices from an artificial neural network model.
\newblock {\em J. Compu. Biol. Chem.}, 27:93--102, 2003.

\bibitem{TaylorWRet03a}
W.~R. Taylor, B.~Xiao, S.~J. Gamblin, and K.~Lin.
\newblock A knot or not a knot? {SET}ting the record `straight' on proteins.
\newblock {\em Comp. Biol. Chem.}, 27:11--15, 2003.

\bibitem{MombelliEet03a}
E.~Mombelli, R.~Morris, W.~R. Taylor, and F.~Fraternali.
\newblock Hydrogen-bonding propensities of sphingomyelin in solution and in a
  bilayer assembly: a molecular dynamics study.
\newblock {\em Biophys. J.}, 84:1507--1517, 2003.

\bibitem{TaylorWRet03b}
W.~R. Taylor and K.~Lin.
\newblock A tangled problem.
\newblock {\em Nature}, 421:25, 2003.
\newblock (concept).

\bibitem{StevensAet04}
A.~Stevens, , M.~Bock, S.~Ellis, P.~Le~Tissier, K.~N. Bishop, W.~R. Taylor, and
  J.~P. Stoye.
\newblock Retroviral capsid determinants of the {Fv1 NB-} and {NR-} tropism.
\newblock {\em J. Virology}, 78:9592--9598, 2004.

\bibitem{TaylorWRet04b}
W.~R. Taylor and J.~P. Stoye.
\newblock Consensus molecular models for the amino terminal domain of the
  retrovirus restriction gene {\em fv1} and the murine leukaemia virus capsid
  proteins.
\newblock {\em JMC Struc. Biology}, 4:1--15, 2004.

\end{thebibliography}
