\documentstyle[a4,12pt]{report}
\begin{document}
{\bf \LARGE
William R.~Taylor: publication list 2007\\ \\ \\
}
{\bf \large
Summary of publications:\\
}
195 papers published of which 14 appeared in the journal {\em Nature}.\\ \\
125 papers are refereed research reports of which 16 were in the
{\em Journal of Molecular Biology}.
Another 45 appeared in major protein and bioinformatics journals.\\ \\
Two books have been edited and two co-authored.
\begin{itemize}
\item
W.~R. Taylor, editor.
\newblock {\em Patterns in Protein sequence and Structure}, volume~7 of {\em
  Springer series in Biophysics (ed. Bayley, P. M.)}.
\newblock Springer-Verlag, Heidelberg, 1992.
\item
D.~Higgins and W.~Taylor, editors.
\newblock {\em Bioinformatics: Sequence structure and databases}.
\newblock Oxford University Press, 2000.
\item
I.~Eidhammer, I.~Jonassen, and W.~R. Taylor.
\newblock {\em Protein Bioinformatics: an algorithmic approach to sequence and
  structure analysis}.
\newblock J. Wiley, London, 2004.
\item
W.~R. Taylor and A.~Asz\'odi.
\newblock {\em Protein Geometry, Classification, Topology and Symmetry}.
\newblock CRC Press, 2005.
\end{itemize}
{\bf \large
Summary of citations:\\
}
A search over a citation database\footnote{
{\tt http://portal.isiknowledge.com} using a simple author search and removing
false hits by hand.  Two corrections were made for an incorrect year and spelling
in refs. 18 and 42 (in main bibliography).
}
found 132 of the 195 publications with a total of over 9000 citations giving an
average of 68.5 citations per paper.   These break-down as:\\ \\
\begin{centering}
\begin{tabular}{r|ccccc}
\hline
citations & $\ge$10 & $\ge$50 & $\ge$100 & $\ge$200 & $\ge$500 \\
papers    &      85 &      42 &       23 &       13 &        4 \\
\hline
\end{tabular}
\end{centering}
\clearpage
\include{select.bbl}
\end{document}
