\begin{thebibliography}{100}

\bibitem{CohenFEet80a}
F.~E. Cohen, M.~J.~E. Sternberg, and W.~R. Taylor.
\newblock Analysis and prediction of the stacking of $\beta$-pleated sheets.
\newblock In R.~Jainikie, editor, {\em Protein Folding}, pages 131--148.
  Elsivier, Amsterdam, 1980.

\bibitem{CohenFEet80b}
F.~E. Cohen, M.~J.~E. Sternberg, and W.~R. Taylor.
\newblock Analysis and prediction of protein $\beta$-sheet structures by a
  combinatorial approach.
\newblock {\em Nature}, 285:378--382, 1980.

\bibitem{CohenFEet81}
F.~E. Cohen, M.~J.~E. Sternberg, and W.~R. Taylor.
\newblock Analysis of the tertiary structure of protein $\beta$-sheet
  sandwiches.
\newblock {\em J. Molec. Biol.}, 148:253--272, 1981.

\bibitem{TaylorWR81}
W.~R. Taylor.
\newblock {\em Analysis and Prediction of Protein Structure}.
\newblock PhD thesis, Department of Zoology (Lab. of Molecular Biophysics),
  University of Oxford, 1981.

\bibitem{SternbergMJEet81}
M.~J.~E. Sternberg, F.~E. Cohen, W.~R. Taylor, and R.~J. Feldmann.
\newblock Analysis and prediction of structural motifs in the glycolytic
  enzymes.
\newblock {\em Proc. Roy. Soc. Lond. B}, 293:177--189, 1981.

\bibitem{CohenFEet82a}
F.~E. Cohen, M.~J.~E. Sternberg, and W.~R. Taylor.
\newblock Analysis and prediction of the packing of $\alpha$-helices against a
  $\beta$-sheet in the tertiary structure of globular proteins.
\newblock {\em J. Molec. Biol.}, 156:821--862, 1982.

\bibitem{SternbergMJEet82a}
M.~J.~E. Sternberg, F.~E. Cohen, and W.~R. Taylor.
\newblock A combinatorial approach to the prediction of the tertiary fold of
  globular proteins.
\newblock {\em Biochem. Soc. Trans.}, 10, 1982.

\bibitem{TaylorWRet83a}
W.~R. Taylor and J.~M. Thornton.
\newblock Prediction of super-secondary structure in proteins.
\newblock {\em Nature}, 301:540--542, 1983.

\bibitem{TaylorWRet83b}
W.~R. Taylor, J.~M. Thornton, and W.~G. Turnell.
\newblock A ellipsoidal approximation of protein shape.
\newblock {\em J. Molec. Graphics}, 1:30--38, 1983.

\bibitem{SternbergMJEet84}
M.~J.~E. Sternberg and W.~R. Taylor.
\newblock Modelling the {ATP}-binding site of oncogene products.
\newblock {\em FEBS Lett.}, 175:387--392, 1984.

\bibitem{TaylorWR84}
W.~R. Taylor.
\newblock An algorithm to compare secondary structure predictions.
\newblock {\em J. Molec. Biol.}, 173:513--514, 1984.
\newblock (appendix).

\bibitem{TaylorWRet84}
W.~R. Taylor and J.~M. Thornton.
\newblock Recognition of super-secondary structure in proteins.
\newblock {\em J. Molec. Biol.}, 173:487--514, 1984.

\bibitem{GarrattRCet85}
R.~C. Garratt, W.~R. Taylor, and J.~M. Thornton.
\newblock The influence of tertiary structure on secondary structure
  prediction: accessibility versus predictability for beta-structure.
\newblock {\em FEBS Lett.}, 188:59--62, 1985.

\bibitem{ThorntonJMet85}
J.~M. Thornton, B.~L. Sibanda, and W.~R. Taylor.
\newblock Variability, modelling and prediction of $\beta$-hairpins with
  reference to the immunoglobulin fold.
\newblock In E.~Reid, G.~M.~W. Cook, and D.~J. Morre, editors, {\em
  Investigation and exploitation of antibody combining sites}, pages 23--31.
  Plenum Pub. Corp., N.Y., 1985.

\bibitem{SternbergMJEet85a}
M.~J.~E. Sternberg and W.~R. Taylor.
\newblock Modelling {SRC} and the {EGF} receptors by computer graphics.
\newblock {\em Brit. J. Cancer}, 52:411, 1985.
\newblock (abstract).

\bibitem{SternbergMJEet85b}
M.~J.~E. Sternberg, W.~R. Taylor, J.~Nyakairu, J.~Fox, and C.~J. Rawlings.
\newblock Reasoning about protein topology using the logic programming language
  {PROLOG}.
\newblock {\em J. Molec. Graph.}, 3:108--109, 1985.
\newblock (abstract).

\bibitem{RawlingsCJet85b}
C.~J. Rawlings, W.~R. Taylor, J.~Nyakairu, J.~Fox, and M.~J.~E. Sternberg.
\newblock Reasoning about protein topology using the logic programming language
  {PROLOG}.
\newblock {\em J. Molec. Graph.}, 3:151--157, 1985.

\bibitem{BlundellTLet86}
T.~L. Blundell, D.~Barlow, B.~L. Sibanda, J.~M. Thornton, W.~R. Taylor, I.~J.
  Tickle, M.~J.~E. Sternberg, J.~E. Pitts, I.~Haneef, and A.~M. Hemmings.
\newblock Three-dimensional structural aspects of the design of new proteins.
\newblock {\em Phil. Trans. Roy. Soc. (Lond.)}, A317:333--344, 1986.

\bibitem{NikasIet86}
I.~Nikas, J.~McLauchlan, A.~J. Davison, W.~R. Taylor, and J.~B. Clemments.
\newblock Predicted structural features of ribonucleotide reductase.
\newblock {\em Proteins}, 1, 1986.

\bibitem{BarlowDJet86}
D.~J. Barlow, T.~L. Blundell, M.~S. Edwards, B.~L. Sibanda, M.~J.~E. Sternberg,
  W.~R. Taylor, and J.~M. Thornton.
\newblock The analysis of homologous tertiary structures and the design of
  novel proteins.
\newblock In M.~Inouye and R.~Sarma, editors, {\em Protein Engineering:
  Applications in Science, Medicine, and Industry}, chapter~3, pages 29--40.
  Academic Press (Inc.), Orlando, USA, 1986.

\bibitem{GreenNMet86}
N.~M. Green, W.~R. Taylor, C.~J. Brandl, B.~Korczak, and D.~H.~A. MacLennan.
\newblock Structural and mechanistic implications of the amino acid sequence of
  calcium transporting {ATP}ases.
\newblock In C.~Evered, editor, {\em Calcium and the Cell}, volume 122 of {\em
  Ciba Found. Symp.}, pages 93--113. J. Wiley and Son, 1986.

\bibitem{ThorntonJMet86}
J.~M. Thornton, M.~S. Edwards, W.~R. Taylor, and D.~J. Barlow.
\newblock Location of 'continuous' antigenic determinants in the protuding
  regions of proteins.
\newblock {\em EMBO J.}, 5:409--413, 1986.

\bibitem{RothbardJBet86}
J.~B. Rothbard, A.~Townsend, M.~Edwards, and W.~R. Taylor.
\newblock Pattern recognition among {T}-cell epitopes.
\newblock In {\em Modern trends in human leukemia}, volume VII. Elsevier,
  Amsterdam, 1986.

\bibitem{KnottTJet86}
T.~J. Knott, R.~J. Pease, L.~M. Powell, S.~C. Wallis, S.~C. Rall, T.~L.
  Innerarity, B.~Blackhart, W.~R. Taylor, A.~J. Lusis, B.~J. McCarthy, R.~W.
  Mahley, B.~Levy-Wilson, and J.~Scott.
\newblock Human apolipoprotein {B}: complete c{DNA} sequence and idenification
  of structural domains in the protein.
\newblock {\em Nature}, 323:734--738, 1986.
\newblock (Taylor, W. R. is misprinted as Taylor, W. H. in the journal).

\bibitem{RawlingsCJet86a}
C.~J. Rawlings, W.~R. Taylor, J.~Nyakairu, J.~Fox, and M.~J.~E. Sternberg.
\newblock Using {PROLOG} to represent and reason about protein structure.
\newblock {\em Lecture Notes in Computer Science}, 1986.

\bibitem{TaylorWR86a}
W.~R. Taylor.
\newblock Identification of protein sequence homology by consensus template
  alignment.
\newblock {\em J. Molec. Biol.}, 188:233--258, 1986.

\bibitem{TaylorWR86b}
W.~R. Taylor.
\newblock The classification of amino acid conservation.
\newblock {\em J. Theor. Biol.}, 119:205--218, 1986.

\bibitem{TaylorWR86c}
W.~R. Taylor.
\newblock Toward a practical grammar of protein structure: protein structure
  prediction by template fitting.
\newblock In R.~Fletterick and M.~Zoller, editors, {\em Computer Graphics and
  Molecular Modeling}, Current Communications in Molecular Biology, chapter~14,
  pages 77--84. Cold Spring Harbor Laboratory, New-York, 1986.

\bibitem{TaylorWR86d}
W.~R. Taylor.
\newblock A general algorithm for the recognition of sequence patterns in
  globular proteins.
\newblock {\em J. Molec. Biol.}, 188:254--258, 1986.
\newblock (appendix).

\bibitem{GeisowMJet87}
M.~J. Geisow, J.~H. Walker, C.~Boustead, and W.~R. Taylor.
\newblock Anexins --- a new family of {C}a$^{2+}$-regulated
  phospholipid-binding proteins.
\newblock {\em Bioscience Reports}, 7:289--298, 1987.

\bibitem{ZvelebilMJet87}
M.~J. Zvelebil, G.~J. Barton, W.~R. Taylor, and M.~J.~E. Sternberg.
\newblock Prediction of protein secondary structure and active sites using the
  alignment of homologous sequences.
\newblock {\em J. Molec. Biol.}, 195:957--961, 1987.

\bibitem{TaylorWR87}
W.~R. Taylor.
\newblock Multiple sequence alignment by a pairwise algorithm.
\newblock {\em Comp. App. Bio. Sci.}, 3:81--87, 1987.

\bibitem{BajajMet87}
M.~Bajaj, M.~Waterfield, J.~Schlessinger, W.~R. Taylor, and T.~L. Blundell.
\newblock On the tertiary structures of the extracellular domains of the {EGF}
  and insulin receptors.
\newblock {\em Biochim. Biophys. Acta}, 916:220--226, 1987.

\bibitem{TaylorWRet87}
W.~R. Taylor and M.~J. Geisow.
\newblock A predicted structure for the calcium dependant membrane binding
  proteins p32, p35 and p36.
\newblock {\em Prot. Eng.}, 1:183--187, 1987.

\bibitem{PearlLHet87a}
L.~H. Pearl and W.~R. Taylor.
\newblock Sequence specificity of retroviral proteases.
\newblock {\em Nature}, 328:482, 1987.
\newblock (Communication).

\bibitem{EngelJet87b}
J.~Engel, W.~R. Taylor, M.~Paulsson, H.~Sage, and B.~Hogan.
\newblock Calcium binding domains and calcium induced conformational transition
  of {SPARC/BM-40/osteonectin}, an extracellular glycoprotein expressed in
  mineralized and nonmineralized tissues.
\newblock {\em Biochemistry}, 26:6958--6965, 1987.

\bibitem{PearlLHet87b}
L.~H. Pearl and W.~R. Taylor.
\newblock A structural model for the retroviral proteases.
\newblock {\em Nature}, 329:351--354, 1987.

\bibitem{GreenNMet88}
N.~M. Green, W.~R. Taylor, and D.~H.~A. MacLennan.
\newblock A consensus structure for cation pumps.
\newblock In W.~D. Stein and S.~J.~D. Karlish, editors, {\em Ion Pumps}, Prog.
  Clin. Biol. Res., pages 15--24. Alan R. Liss, New York, 1988.

\bibitem{RodriguesVet88}
V.~Rodrigues, M.~Chaudhri, M.~Knight, H.~Meadows, A.~E. Chambers, W.~R. Taylor,
  C.~Kelly, and A.~J.~G. Simpson.
\newblock Predicted structure of a major {{\em Schistosoma mansoni}} eggshell
  protein.
\newblock {\em Molec. Biochem. Parasitology}, 32:7--14, 1988.

\bibitem{TaylorSAet88}
S.~A. Taylor, J.~Lewis, J.~Pacy, W.~R. Taylor, and R.~G. Price.
\newblock Glomerular basement membrane thickness in male and female rats fed
  sucrose-rich diets.
\newblock In M.~C. Gubler and M.~Sternberg, editors, {\em Progress in Basement
  Membrane Research: Renal and related aspects in health and disease}, pages
  205--209. John Libbey, Eurotext Ltd., 1988.

\bibitem{TaylorWR88a}
W.~R. Taylor.
\newblock A flexible method to align large numbers of biological sequences.
\newblock {\em J. Molec. Evol.}, 28:161--169, 1988.
\newblock The correct year is 1989.

\bibitem{RothbardJBet88a}
J.~B. Rothbard, R.~I. Lechler, K.~Howland, V.~Bal, D.~D. Eckels, R.~Sekaly,
  E.~O. Long, W.~R. Taylor, and J.~R. Lamb.
\newblock A structural model of {HLA-DR1} restricted {T}-cell antigen
  recognition.
\newblock {\em Cell}, 52:515--523, 1988.

\bibitem{TaylorWR88b}
W.~R. Taylor.
\newblock Pattern matching methods in protein sequence comparison and structure
  prediction.
\newblock {\em Prot. Engng.}, 2:77--86, 1988.

\bibitem{RothbardJBet88b}
J.~B. Rothbard and W.~R. Taylor.
\newblock A sequence pattern common to {T}-cell epitopes.
\newblock {\em EMBO J.}, 7:93--100, 1988.

\bibitem{TaylorWR88c}
W.~R. Taylor.
\newblock Macromolecular structure and specificity.
\newblock {\em Speculations in Science and Technology}, 11:79--80, 1988.
\newblock (book review).

\bibitem{TaylorWR89}
W.~R. Taylor.
\newblock A template based method of pattern matching in protein sequences.
\newblock {\em Prog. Biophys. Molec. Biol.}, 54:159--252, 1989.

\bibitem{TaylorWRet89a}
W.~R. Taylor and C.~A. Orengo.
\newblock Protein structure alignment.
\newblock {\em J. Molec. Biol.}, 208:1--22, 1989.

\bibitem{RothbardJBet89a}
J.~B. Rothbard, R.~Busch, K.~Howland, V.~Bal, C.~Fenton, W.~R. Taylor, and
  J.~R. Lamb.
\newblock Structural analysis of a peptide -- {HLA} class {II} complex:
  identification of critical interaactions for its formation and recognition by
  {T}-cell receptor.
\newblock {\em Int. Immunology}, 1:479--486, 1989.

\bibitem{TaylorWRet89b}
W.~R. Taylor and C.~A. Orengo.
\newblock A holistic approach to protein structure comparison.
\newblock {\em Prot. Eng.}, 2:505--519, 1989.

\bibitem{RothbardJBet89b}
J.~B. Rothbard, H.~C. Bodmer, K.~Howland, R.~M. Pemberton, B.~E. Askonas, and
  W.~R. Taylor.
\newblock {T}-cell recognition of a peptide/{H2-Kd} complex.
\newblock {\em EMBO J.}, 8:2321--2328, 1989.

\bibitem{ThorntonJMet89b}
J.~M. Thornton and W.~R. Taylor.
\newblock Protein structure prediction.
\newblock In J.~B.~C. Findlay and M.~J. Geisow, editors, {\em Protein
  Sequencing: A Practical Approach}, chapter~7, pages 147--190. IRL Press,
  Oxford, 1989.

\bibitem{TaylorWRet89c}
W.~R. Taylor and N.~M. Green.
\newblock The predicted secondary structures of the nucleotide-binding sites of
  six cation-transporting {ATPases} lead to a probable tertiary fold.
\newblock {\em Eur. J. Biochem.}, 179:241--248, 1989.

\bibitem{TaylorWRet90}
W.~R. Taylor, C.~A. Orengo, and L.~H. Pearl.
\newblock Comparison of predicted and {X}-ray crystal structures of retroviral
  proteases.
\newblock In M.~Ikehara, editor, {\em Protein engineering: protein design in
  basic research, medicine, and industry}, pages 21--27. Japan Scientific
  Press, Tokyo; Springer-Verlag, Berlin, 1990.

\bibitem{KellyCet90}
C.~Kelly, P.~Evans, J.~K.~C. Ma, L.~A. Bergmeier, W.~R. Taylor, L.~J. Brady,
  S.~F. Lee, A.~S. Bleiweis, and T.~Lehner.
\newblock Sequencing and characterization of the 185 {KD}a cell-surface antigen
  of {{\em Streptococcus mutans}}.
\newblock {\em Archives of Oral Biology}, 35 S, 1990.

\bibitem{OrengoCAet90a}
C.~A. Orengo and W.~R. Taylor.
\newblock A rapid method for protein structure alignment.
\newblock {\em J. Theor. Biol.}, 147:517--551, 1990.

\bibitem{TaylorWR90a}
W.~R. Taylor.
\newblock Hierarchical method to align large numbers of biological sequences.
\newblock In R.~F. Doolittle, editor, {\em Molecular Evolution: computer
  analysis of protein and nucleic acid sequences}, volume 183 of {\em Meth.
  Enzymol.}, chapter~29, pages 456--474. Academic Press, San Diego, CA, USA.,
  1990.

\bibitem{TaylorWR90b}
W.~R. Taylor.
\newblock Comparison of predicted and {X}-ray crystal structures of retroviral
  proteases.
\newblock {\em Prot. Engng.}, 3:282, 1990.
\newblock (abstract).

\bibitem{TaylorWRet91}
W.~R. Taylor and D.~T. Jones.
\newblock Templates, consensus patterns and motifs.
\newblock {\em Current Opinion in Struct. Biol.}, 1:327--333, 1991.

\bibitem{GarrattRet91}
R.~Garratt, J.~M. Thornton, and W.~R. Taylor.
\newblock An extension of secondary structure prediction towards the prediction
  of tertiary structure.
\newblock {\em FEBS Lett.}, 208:141--146, 1991.

\bibitem{TaylorWR91a}
W.~R. Taylor.
\newblock Sequence analysis: spinning in hyperspace.
\newblock {\em Nature}, 353:388--389, 1991.
\newblock (News and Views).

\bibitem{RippmannFet91a}
F.~Rippmann and W.~R. Taylor.
\newblock Visualization of structural similarity in proteins.
\newblock {\em J. Molec. Graph.}, 9:3--16, 1991.

\bibitem{RippmannFet91b}
F.~Rippmann, W.~R. Taylor, J.~B. Rothbard, and N.~M. Green.
\newblock A hypothetical model for the peptide binding domain of hsp70 based on
  the peptide binding domain of {HLA}.
\newblock {\em EMBO Journal}, 10:5--10, 1991.

\bibitem{LaPollaRJet91b}
R.~J. La~Polla, J.~A. Haron, C.~G. Kelly, W.~R. Taylor, Bohart C.,
  M.~Hendricks, J.~Pyati, R.~T. Graff, J.~K.~C. Ma, and T.~Lehner.
\newblock Sequence and structural analysis of surface protein antigen-{I/II
  (SPAA)} of {{\em Streptococcus sobrinus}}.
\newblock {\em Infection and Immunity;}, 59:2677--2685, 1991.

\bibitem{TaylorWR91b}
W.~R. Taylor.
\newblock Towards protein tertiary fold prediction using distance and motif
  constraints.
\newblock {\em Prot. Engng.}, 4:853--870, 1991.

\bibitem{OrengoCAet92}
C.~A. Orengo, N.~P. Brown, and W.~R. Taylor.
\newblock Fast protein structure comparison for databank searching.
\newblock {\em Prot. Struct. Funct. Genet.}, 14:139--167, 1992.

\bibitem{TaylorWR92a}
W.~R. Taylor, editor.
\newblock {\em Patterns in Protein sequence and Structure}, volume~7 of {\em
  Springer series in Biophysics (ed. Bayley, P. M.)}.
\newblock Springer-Verlag, Heidelberg, 1992.

\bibitem{JonesDTet92a}
D.~T. Jones, W.~R. Taylor, and J.~M. Thornton.
\newblock The rapid generation of mutation data matrices from protein
  sequences.
\newblock {\em Comp. App. Bio. Sci.}, 8:275--282, 1992.

\bibitem{TaylorWR92b}
W.~R. Taylor.
\newblock Patterns, predictions and problems (introduction).
\newblock In W.~R. Taylor, editor, {\em Patterns in Protein sequence and
  Structure}, volume~7 of {\em Springer series in Biophysics (ed. Bayley, P.
  M.)}, pages 1--9. Springer-Verlag, Heidelberg, 1992.

\bibitem{JonesDTet92b}
D.~T. Jones, W.~R. Taylor, and J.~M. Thornton.
\newblock A new approach to protein fold recognition.
\newblock {\em Nature}, 358:86--89, 1992.

\bibitem{TaylorWR92c}
W.~R. Taylor.
\newblock New paths from dead ends.
\newblock {\em Nature}, 356:478--479, 1992.
\newblock (News and Views).

\bibitem{TaylorWR92d}
W.~R. Taylor.
\newblock Sequencing and computer time.
\newblock {\em Science}, 258:1421, 1992.
\newblock (Letter).

\bibitem{LaThangueNBet93}
N.~B. LaThangue and W.~R. Taylor.
\newblock A structural similarity between mamalian and yeast transcription
  factors for cell-cycle-regulated genes.
\newblock {\em Trends in Cell Biol.}, 3:75--76, 1993.

\bibitem{TaylorWR93a}
W.~R. Taylor.
\newblock Protein fold refinement: building models from idealised folds using
  motif constraints and multiple sequence data.
\newblock {\em Prot. Engng.}, 6:593--604, 1993.

\bibitem{TaylorWRet93a}
W.~R. Taylor and D.~T. Jones.
\newblock Deriving an amino acid distance matrix.
\newblock {\em J. Theor. Biol.}, 164:65--83, 1993.

\bibitem{AszodiAet93a}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Connection topology of proteins.
\newblock {\em Comp. App. Bio. Sci.}, 9:523--529, 1993.

\bibitem{JonesDTet93a}
D.~T. Jones, C.~A. Orengo, W.~R. Taylor, and J.~M. Thornton.
\newblock Progress towards recognising protein folds from amino acid sequence.
\newblock {\em Prot. Engng.}, 6 (supplement):124, 1993.
\newblock (abstract).

\bibitem{OrengoCAet93a}
C.~A. Orengo, T.~P. Flores, D.~T. Jones, W.~R. Taylor, and J.~M. Thornton.
\newblock Recurring structural motifs in proteins with different functions.
\newblock {\em Current Biology}, 3:131--139, 1993.

\bibitem{TaylorWR93b}
W.~R. Taylor.
\newblock Modelling protein structure from remote sequence similarity: an
  approach to tertiary structure prediction.
\newblock In S.~Suhai, editor, {\em Computational methods in genome research},
  pages 317--328. Plenum Pub. Corp., 1993.

\bibitem{OrengoCAet93b}
C.~A. Orengo and W.~R. Taylor.
\newblock A local alignment method for protein structure motifs.
\newblock {\em J. Molec. Biol.}, 233:488--497, 1993.

\bibitem{TaylorWRet93b}
W.~R. Taylor, D.~T. Jones, and A.~W. Segal.
\newblock A structural model for the nucleotide binding domain of the
  cytochrome $b_{-245}$ $\beta$-chain.
\newblock {\em Protein Science}, 2:1675--1685, 1993.

\bibitem{OrengoCAet93c}
C.~A. Orengo, T.~P. Flores, W.~R. Taylor, and J.~M. Thornton.
\newblock Identification and classification of protein fold families.
\newblock {\em Prot. Engng.}, 6:485--500, 1993.

\bibitem{TaylorWR93d}
W.~R. Taylor.
\newblock Modelling protein structure from remote sequence similarity.
\newblock In R.~Lavery and E.~Westhof, editors, {\em Molecular modelling and
  graphics applied to structure-function relationships}. INSERM, Paris, 1993.

\bibitem{TaylorWR93e}
W.~R. Taylor.
\newblock Protein structure prediction from sequence.
\newblock {\em Computers and Chem.}, 17:117--122, 1993.

\bibitem{StokesDLet94}
D.~L. Stokes, W.~R. Taylor, and N.~M. Green.
\newblock Structure, transmembrane topology and helix packing of {P}-type ion
  pumps.
\newblock {\em FEBS Lett.}, 346:32--38, 1994.

\bibitem{BhattacharyaSet94}
S.~Bhattacharya, N.~Navaratnam, J.~R. Morrison, J.~Scott, and W.~R. Taylor.
\newblock Cytosine nucleoside/nucleotide deaminases and apolipoprotein {B}
  m{RNA} editing.
\newblock {\em TIBS}, pages 105--106, 1994.

\bibitem{ThorntonJMet94}
J.~M. Thornton, C.~M. Orengo, D.~T. Jones, and W.~R. Taylor.
\newblock Protein motifs and folding recognition.
\newblock {\em Biophys. J.}, page 241, 1994.
\newblock (abstract).

\bibitem{ChothiaCet94}
C.~Chothia and W.~R. Taylor.
\newblock Sequences and topology.
\newblock {\em Curr. Op. Struct. Biol.}, 4:381--382, 1994.
\newblock (editorial overview).

\bibitem{TaylorWR94a}
W.~R. Taylor.
\newblock Protein structure modelling from remote sequence similarity.
\newblock {\em J. Biotechnology}, 12:281--291, 1994.
\newblock Special issue: {\em Genome Research/Molecular Biotechnology}, Part 1.
  ed., Helmut Bl{\"o}cker.

\bibitem{JonesDTet94a}
D.~T. Jones, W.~R. Taylor, and J.~M. Thornton.
\newblock A mutation data matrix for transmembrane proteins.
\newblock {\em FEBS Lett.}, pages 269--275, 1994.

\bibitem{TaylorWRet94a}
W.~R. Taylor, D.~T. Jones, and N.~M. Green.
\newblock A method for $\alpha$-helical integral membrane protein fold
  prediction.
\newblock {\em Prot. Struct. Funct. Genet.}, 18:281--294, 1994.

\bibitem{HatrickKet94a}
K.~Hatrick and W.~R. Taylor.
\newblock Sequence conservation and correlation measures in protein structure
  prediction.
\newblock {\em Computers Chem.}, 18:245--250, 1994.

\bibitem{OrengoCAet94a}
C.~A. Orengo, T.~P. Flores, W.~R. Taylor, and J.~M. Thornton.
\newblock Protein fold families and structural motifs.
\newblock In {\em Proceedings of the {NATO ARW} workshop on statistical
  mechanics, protein structure and protein substrate interactions}, 1994.

\bibitem{AszodiAet94a}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Folding polypeptide $\alpha$-carbon backbones by distance geometry
  methods.
\newblock {\em Biopolymers}, 34:489--506, 1994.

\bibitem{TaylorWRet94b}
W.~R. Taylor and A.~Asz\'{o}di.
\newblock Building protein folds using distance geometry: towards a general
  modeling and prediction method.
\newblock In K.~M. Merz and S.~M. Le{G}rand, editors, {\em The protein folding
  problem and tertiary structure prediction}, chapter~6, pages 165--192.
  Birkh{\"{a}}user (Springer-Verlag), Boston, MA., USA, 1994.

\bibitem{JonesDTet94b}
D.~T. Jones, W.~R. Taylor, and J.~M. Thornton.
\newblock A model recognition approach to the prediction of all-helical
  membrane protein structure and topology.
\newblock {\em Biochemistry}, 33:3038--3049, 1994.

\bibitem{AszodiAet94b}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Secondary structure formation in model polypeptide chains.
\newblock {\em Prot. Engng.}, 7:633--644, 1994.

\bibitem{TaylorWR94b}
W.~R. Taylor.
\newblock Remotely related sequences and structures: analysis and predictive
  modelling.
\newblock {\em Trends Biotech.}, 12:154--157, 1994.

\bibitem{TaylorWRet94c}
W.~R. Taylor and K.~Hatrick.
\newblock Compensating changes in protein multiple sequence alignments.
\newblock {\em Prot. Engng.}, 7:341--348, 1994.

\bibitem{TaylorWR94c}
W.~R. Taylor.
\newblock Motif-biased protein sequence alignment.
\newblock {\em J. Comp. Biol.}, 1:297--311, 1994.

\bibitem{AszodiAet94c}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Modelling secondary structure formation by distance geometry
  techniques.
\newblock In H.~Bohr and S.~Brunak, editors, {\em Distance based approaches to
  protein structure determination}, pages 222--236. IOS press, Elsevier
  (Amsterdam), 1994.

\bibitem{TaylorWRet94d}
W.~R. Taylor, T.~P. Flores, and C.~A. Orengo.
\newblock Multiple protein structure alignment.
\newblock {\em Prot. Sci.}, 3:1858--1870, 1994.

\bibitem{TaylorWRet94e}
W.~R. Taylor and A.~Asz\'{o}di.
\newblock Modelling and predicting protein structure using distance geometry.
\newblock In H.~Bohr and S.~Brunak, editors, {\em Distance based approaches to
  protein structure determination}, pages 213--221. IOS press, Elsevier
  (Amsterdam), 1994.

\bibitem{TaylorWRet95a}
W.~R. Taylor and D.~T. Jones.
\newblock Modelling and predicting $\alpha$-helical transmembrane structures.
\newblock In H.~Bohr and S.~Brunak, editors, {\em Protein Folds: A Distance
  Based Approach}, pages 283--293. CRC Press Inc., Boca Raton, Florida, U.S.A.,
  1995.

\bibitem{AszodiAet95a}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Estimating polypeptide $\alpha$-carbon distances from multiple
  sequence alignments.
\newblock {\em J. Math. Chem.}, 17:167--184, 1995.

\bibitem{TaylorWR95a}
W.~R. Taylor.
\newblock An investigation of conservation-biased gap-penalties for multiple
  protein sequence alignment.
\newblock {\em Gene}, 165:GC27--35, 1995.
\newblock Internet journal Gene Combis: {\tt
  http://www.elsevier.nl/locate/genecombis}.

\bibitem{TaylorWR95b}
W.~R. Taylor.
\newblock Sequence alignment of proteins and nucleic acids.
\newblock In R.~A. Meyers, editor, {\em Molecular Biology and Biotechnology:
  comprehensive desk reference}, pages 856--859. VCH, New York, USA, 1995.

\bibitem{TaylorWRet95b}
W.~R. Taylor and N.~M. Green.
\newblock {\em Structure in Protein Chemistry} (by {J.~Kyte}).
\newblock {\em Nature}, 375:372, 1995.
\newblock (book review).

\bibitem{AszodiAet95b}
A.~Asz\'{o}di, M.~J. Gradwell, and W.~R. Taylor.
\newblock Protein fold determination using a small number of distance
  restraints.
\newblock In H.~Bohr and S.~Brunak, editors, {\em Protein Folds: A Distance
  Based Approach}, pages 85--97. CRC Press Inc., Boca Raton, Florida, U.S.A.,
  1995.

\bibitem{AszodiAet95c}
A.~Asz\'{o}di, M.~J. Gradwell, and W.~R. Taylor.
\newblock Global fold determination from a small number of distance restraints.
\newblock {\em J. Molec. Biol.}, 251:308--326, 1995.

\bibitem{BrownNPet96}
N.~P. Brown, C.~A. Orengo, and W.~R. Taylor.
\newblock A protein structure comparison methodology.
\newblock {\em Computers Chem.}, 20:359--380, 1996.

\bibitem{OrengoCAet96}
C.~A. Orengo and W.~R. Taylor.
\newblock {SSAP}: sequential structure alignment program for protein structure
  comparison.
\newblock In R.~F. Doolittle, editor, {\em Computer methods for macromolecular
  sequence analysis}, volume 266 of {\em Meth. Enzymol.}, pages 617--635.
  Academic Press, Orlando, FA, USA., 1996.

\bibitem{TaylorWR96a}
W.~R. Taylor.
\newblock A non-local gap-penaly for profile alignment.
\newblock {\em Bull. Math. Biol.}, 58:1--18, 1996.

\bibitem{AszodiAet96a}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Homology modelling by distance geometry.
\newblock {\em Folding \& Design}, 1:325--334, 1996.

\bibitem{WernerEet96a}
E.~Werner, A.~A. Holder, A.~Asz\'{o}di, and W.~R. Taylor.
\newblock A novel 11-residue coilled-coil motif predicts a histidine zipper.
\newblock {\em Prot. Pept. Lett.}, 3:139--146, 1996.

\bibitem{TaylorWR96b}
W.~R. Taylor.
\newblock Multiple protein sequence alignment: algorithms for gap insertion.
\newblock In R.~F. Doolittle, editor, {\em Computer methods for macromolecular
  sequence analysis}, volume 266 of {\em Meth. Enzymol.}, pages 343--367.
  Academic Press, Orlando, FA, USA., 1996.

\bibitem{TaylorWR96c}
W.~R. Taylor.
\newblock Sequence alignment of proteins and nucleic acids.
\newblock In R.~A. Meyers, editor, {\em Encyclopedia of Molecular Biology and
  Molecular Medicine}, volume~5, pages 419--428. VCH, New York, USA, 1997.

\bibitem{HeringaJet97}
J.~Heringa and W.~R. Taylor.
\newblock Three-dimensional domain duplication, swapping and stealing.
\newblock {\em Curr. Op. Struct. Biol.}, 7:416--421, 1997.

\bibitem{AszodiAet97a}
A.~Asz\'{o}di and W.~R. Taylor.
\newblock Hierarchical inertial projection: a fast distance matrix embedding
  algorithm.
\newblock {\em Computers Chem.}, 21:13--23, 1997.

\bibitem{TaylorWRet97a}
W.~R. Taylor and C.~A. Orengo.
\newblock Protein fold topology and structural families.
\newblock In G.~Allen, editor, {\em Protein: a comprehensive treatise}, pages
  143--169. JAI Press Inc., U.S.A., 1997.

\bibitem{PollockDDet97a}
D.~D. Pollock and W.~R. Taylor.
\newblock Effectiveness of correlation analysis in identifying protein residues
  undergoing correlated evolution.
\newblock {\em Prot. Engng.}, 10:647--657, 1997.

\bibitem{TaylorWR97b}
W.~R. Taylor.
\newblock Random models for double dynamic score normalisation.
\newblock {\em J. Molec. Evol.}, 44:S174--S180, 1997.
\newblock Special issue in memory of Kimura.

\bibitem{AszodiAet97b}
A.~Asz\'{o}di, R.~E.~J. Munro, and W.~R. Taylor.
\newblock Distance based comparative modelling.
\newblock {\em Folding \& Design}, 2, suppl.:S3--S6, 1997.

\bibitem{TaylorWR97c}
W.~R. Taylor.
\newblock Evolution and relationships of protein families.
\newblock In M.~J. Bishop and C.~J. Rawlings, editors, {\em Nucleic acid and
  protein sequence analysis: a practical approach (second edition)}, Practical
  approach (eds. Rickwood, D. and Hames, B. D.), pages 313--340. IRL Press,
  Oxford, 1997.

\bibitem{AszodiAet97c}
A.~Asz\'{o}di, R.~E.~J. Munro, and W.~R. Taylor.
\newblock Protein modelling by multiple sequence threading and distance
  geometry.
\newblock {\em Proteins}, pages 38--42, 1997.

\bibitem{TaylorWRet97c}
W.~R. Taylor and R.~E.~J. Munro.
\newblock Multiple sequence threading: Conditional gap placement.
\newblock {\em Folding \& Design}, 2, suppl.:S33--S39, 1997.

\bibitem{TaylorWR97d}
W.~R. Taylor.
\newblock Multiple sequence threading: an analysis of alignment quality and
  stability.
\newblock {\em J. Molec. Biol.}, 269:902--943, 1997.

\bibitem{TaylorWR97e}
W.~R. Taylor.
\newblock Residual colours: a proposal for aminochromography.
\newblock {\em Prot. Engng.}, 10:743--746, 1997.
\newblock (Forum section).

\bibitem{JonesDTet98}
D.~T. Jones and W.~R. Taylor.
\newblock Towards structural genomics for transmembrane proteins.
\newblock {\em Biochem. Soc. Trans.}, 26:429--438, 1999.

\bibitem{RittingerKet98}
K.~Rittinger, W.~R. Taylor, S.~J. Smerdon, and S.~J. Gamblin.
\newblock Support for shared ancestry of gaps.
\newblock {\em Nature}, 392:448, 1998.

\bibitem{HigginsDGet98}
D.~G. Higgins and W.~R. Taylor.
\newblock Multiple sequence alignment.
\newblock In M.~Crochemore and D.~Gusfield, editors, {\em Protein Sequence and
  Structure}, volume 807 of {\em Lecture Notes in Computer Science}, pages
  237--244. Springer-Verlag, Berlin, 1998.

\bibitem{WernerEet98}
E.~Werner, W.~R. Taylor, and Holder.
\newblock A {\em {p}lasmodium chabaudi} protein contains a repetitive region
  with a predicted spectrin-like structure.
\newblock {\em Molec. Biochem. Parisitology.}, 94:185--196, 1998.

\bibitem{TaylorWR98a}
W.~R. Taylor.
\newblock Dynamic databank searching with templates and multiple alignment.
\newblock {\em J. Molec. Biol.}, 280:375--406, 1998.

\bibitem{MunroREJet99}
R.~E.~J. Munro and W.~R. Taylor.
\newblock Structure prediction and molecular modelling.
\newblock In R.~E. Reid, editor, {\em Peptide and Protein drug analysis}, pages
  115--132. Marcel Dekker, Inc., 1999.

\bibitem{JonassenIet99}
I.~Jonassen, I.~Eidhammer, and W.~R. Taylor.
\newblock Discovery of local packing motifs in protein structures.
\newblock {\em Proteins: struc. funct. gene.}, 34:206--219, 1999.

\bibitem{PollockDDet99a}
D.~D. Pollock, W.~R. Taylor, and N.~Goldman.
\newblock Coevolving protein residues: maximum likelihood identification and
  relationship to structure.
\newblock {\em J. Molec. Biol.}, 287:187--198, 1999.

\bibitem{TaylorWR99a}
W.~R. Taylor.
\newblock Protein structure alignment using iterated double dynamic
  programming.
\newblock {\em Prot. Sci}, 8:654--665, 1999.

\bibitem{TaylorWRet99a}
W.~R. Taylor and N.~P. Brown.
\newblock Iterated sequence databank search methods.
\newblock {\em Comp. Chem.}, 23:365--385, 1999.

\bibitem{TaylorWRet99b}
W.~R. Taylor and N.~P. Brown.
\newblock {QUEST}: an iterated sequence databank search method.
\newblock In S.~Suhai, editor, {\em Genomics and Proteonomics: functional and
  computational aspects}, pages 67--82. Kluwer Acad./Plenum Pub. Corp., 2000.

\bibitem{TaylorWR99b}
W.~R. Taylor.
\newblock Protein structure domain identification.
\newblock {\em Prot. Engng.}, 12:203--216, 1999.

\bibitem{TaylorWR99c}
W.~R. Taylor.
\newblock The properties of amino acids in sequences.
\newblock In M.~J. Bishop, editor, {\em Nucleic acid and protein databases: a
  practical approach (second edition)}, pages 81--103. Academic Press, 1999.
\newblock Chapter 5.

\bibitem{TaylorWRet99c}
W.~R. Taylor, G.~S{\ae}lensminde, and I.~Eidhammer.
\newblock Multiple protein structure alignment using double-dynamic
  programming.
\newblock {\em Comp. Chem.}, 24:3--12, 2000.

\bibitem{EidhammerIet00}
I.~Eidhammer, I.~Jonassen, and W.~R. Taylor.
\newblock Structure comparison and structure patterns.
\newblock {\em J. Compu. Biol.}, 7:658--716, 2000.

\bibitem{JonassenIet00a}
I.~Jonassen, I.~Eidhammer, S.~H. Grindhaug, and W.~R. Taylor.
\newblock Searching the protein structure databank with weak sequence patterns
  and structural constraints.
\newblock {\em J. Molec. Biol.}, 304:599--619, 2000.

\bibitem{TaylorWR00a}
W.~R. Taylor.
\newblock Searching for the ideal forms of proteins.
\newblock {\em Biochem. Soc. Trans.}, 28:264--269, 2000.

\bibitem{HigginsDGet00a}
D.~G. Higgins and W.~R. Taylor.
\newblock Preface.
\newblock In D.~Higgins and W.~Taylor, editors, {\em Bioinformatics: Sequence
  structure and databases}, pages v--ix. Oxford University Press, 2000.

\bibitem{HigginsDGet00b}
D.~G. Higgins and W.~R. Taylor.
\newblock Multiple sequence alignment.
\newblock In D.~M. Webster, editor, {\em Protein structure prediction}, volume
  143 of {\em Methods in Molecular Biology (ed. J.~M.~Walker)}, pages 1--18.
  Humana Press, Totowa, New Jersey, USA, 2000.

\bibitem{TaylorWR00b}
W.~R. Taylor.
\newblock A deeply knotted protein and how it might fold.
\newblock {\em Nature}, 406:916--919, 2000.

\bibitem{TaylorWR00c}
W.~R. Taylor.
\newblock Protein structure.
\newblock In D.~J.~Balding et~al., editor, {\em Handbook of Statistical
  genetics}, pages 209--235. John Wiley and Sons Ltd., 2000.

\bibitem{TaylorWR00d}
W.~R. Taylor.
\newblock Protein structure comparison using {SAP}.
\newblock In D.~M. Webster, editor, {\em Protein structure prediction}, volume
  143 of {\em Methods in Molecular Biology (ed. J.~M.~Walker)}, pages 19--32.
  Humana Press, Totowa, New Jersey, USA, 2000.

\bibitem{OgunMet01}
M.~Ogun, M.~Grainger, W.~R. Taylor, and A.~A. Holder.
\newblock The merozoite surface protein-6 gene codes for a 36 {kDa}-protein
  associated with the {\em plasmodium falciparum} merozoite surface protein-1
  complex.
\newblock {\em Mol. Biochem. Parasitology}, 112:91--101, 2001.

\bibitem{TaylorWR01a}
W.~R. Taylor.
\newblock Defining linear segments in protein structure.
\newblock {\em J. Molec. Biol.}, 310:1135--1150, 2001.

\bibitem{TaylorWRet01b}
W.~R. Taylor, A.~C.~W. May, N.~P. Brown, and A.~Asz\'odi.
\newblock Protein structure: Geometry, topology and classification.
\newblock {\em Rep. Prog. Phys.}, 64:517--590, 2001.

\bibitem{JonassenIet02}
I.~Jonassen, I.~Eidhammer, D.~Conklin, and W.~R. Taylor.
\newblock Structure motif discovery and mining the {PDB}.
\newblock {\em Bioinformatics}, 18:362--367, 2002.

\bibitem{ConklinDet02}
D.~Conklin, I.~Jonassen, R.~Aasland, and W.~R. Taylor.
\newblock Association of nucleotide patterns with gene function classes:
  application to human 3' untranslated sequences.
\newblock {\em Bioinformatics}, 18:182--189, 2002.

\bibitem{TaylorWR02a}
W.~R. Taylor.
\newblock A periodic table for protein structure.
\newblock {\em Nature}, 416:657--660, 2002.

\bibitem{SaldanhaJWet02a}
J.~W. Saldanha, P.~E. Czabotar, A.~J. Hay, and W.~R. Taylor.
\newblock A model for the cytoplasmic domain of the influenza {A} virus {M2}
  channel by analogy to the {HIV-1 Vpu} protein.
\newblock {\em Protein Peptide Letts.}, 9:495--502, 2002.

\bibitem{TaylorWRet02a}
W.~R. Taylor, J.~Heringa, F.~Baud, and T.~P. Flores.
\newblock A {Fourier} analysis of symmetry in protein structure.
\newblock {\em Protein Eng.}, 15:79--89, 2002.

\bibitem{LinKet02a}
K.~Lin, A.~C. May, and W.~R. Taylor.
\newblock Amino acid substitution matrices from an artificial neural network
  model.
\newblock {\em J. Comput Biol.}, 8:471--481, 2002.

\bibitem{LinKet02b}
K.~Lin, A.~C. May, and W.~R. Taylor.
\newblock Threading using neural networks ({TUNE}): the measure of protein
  sequence-structure compatibility.
\newblock {\em Bioinformatics}, 18:1350--1357, 2002.

\bibitem{TaylorWR02b}
W.~R. Taylor.
\newblock Protein structure comparison using bipartite graph matching.
\newblock {\em Mol. Cell. Proteomics}, 1:334--339, 2002.

\bibitem{TaylorWR02c}
W.~R. Taylor.
\newblock Comparing secondary structure `stick' models of proteins using graph
  matching with double dynamic programming.
\newblock In H.~Seidel H.-W.~Mewes, B.~Weiss, editor, {\em Bioinformatics and
  Genome Analysis}, chapter~7, pages 133--148. Springer-Verlag,
  Berlin/Heidelberg, 2002.
\newblock Ernst Schering Research Foundation Workshop Volume 38.

\bibitem{LinKet02c}
K.~Lin, A.~C. May, and W.~R. Taylor.
\newblock Amino acid encoding schemes from protein structural alignments:
  multidimensional vectors to describe residue types.
\newblock {\em J. Theor. Biol.}, 221:361--365, 2002.

\bibitem{LinKet03a}
K.~Lin, W.~R. Taylor, J.~Klienjung, and J.~Heringa.
\newblock {CAO} matrices from an artificial neural network model.
\newblock {\em J. Compu. Biol. Chem.}, 27:93--102, 2003.

\bibitem{PetersenKet03a}
K.~Petersen and W.~R. Taylor.
\newblock Modelling zinc-binding proteins with {GADGET}: Genetic algorithm and
  distance geometry for exploring topology.
\newblock {\em J. Molec. Biol.}, 325:1039--1059, 2003.

\bibitem{TaylorWRet03a}
W.~R. Taylor, B.~Xiao, S.~J. Gamblin, and K.~Lin.
\newblock A knot or not a knot? {SET}ting the record `straight' on proteins.
\newblock {\em Comp. Biol. Chem.}, 27:11--15, 2003.

\bibitem{MombelliEet03a}
E.~Mombelli, R.~Morris, W.~R. Taylor, and F.~Fraternali.
\newblock Hydrogen-bonding propensities of sphingomyelin in solution and in a
  bilayer assembly: a molecular dynamics study.
\newblock {\em Biophys. J.}, 84:1507--1517, 2003.

\bibitem{TaylorWRet03b}
W.~R. Taylor and K.~Lin.
\newblock A tangled problem.
\newblock {\em Nature}, 421:25, 2003.
\newblock (concept).

\bibitem{TaylorWRet03c}
W.~R. Taylor, R.~E.~J. Munro, K.~Petersen, and R.~P. Bywater.
\newblock {\em Ab initio} modelling of the {N}-terminal domain of the secretin
  receptors.
\newblock {\em Comp. Biol. Chem.}, 27:103--114, 2003.

\bibitem{StevensAet04}
A.~Stevens, , M.~Bock, S.~Ellis, P.~Le~Tissier, K.~N. Bishop, W.~R. Taylor, and
  J.~P. Stoye.
\newblock Retroviral capsid determinants of the {Fv1 NB-} and {NR-} tropism.
\newblock {\em J. Virology}, 78:9592--9598, 2004.

\bibitem{MurrayKBet04}
K.~B. Murray, W.~R. Taylor, and J.~M. Thornton.
\newblock Towards the detection and validation of repeats in protein structure.
\newblock {\em Proteins: struct. funct. bioinfo.}, 57:365--380, 2004.

\bibitem{JohannissenLOet04}
L.~O. Johannissen and W.~R. Taylor.
\newblock Protein fold comparison by the alignment of topological strings.
\newblock {\em Prot. Engng.}, 16:949--955, 2004.

\bibitem{EidhammerIet04}
I.~Eidhammer, I.~Jonassen, and W.~R. Taylor.
\newblock {\em Protein Bioinformatics: an algorithmic approach to sequence and
  structure analysis}.
\newblock J. Wiley, London, 2004.
\newblock ISBN: 0-470-84839-1.

\bibitem{TaylorWR04a}
W.~R. Taylor.
\newblock A molecular model for transcription in the {RNA} world based on the
  ribosome large subunit.
\newblock {\em Comp. Biol. Chem.}, 28:313--319, 2004.

\bibitem{TaylorWRet04a}
W.~R. Taylor and I.~Jonassen.
\newblock A structural pattern-based method for protein fold recognition.
\newblock {\em Proteins: struc. funct. bioinf.}, 56:222--234, 2004.

\bibitem{TaylorWRet04b}
W.~R. Taylor and J.~P. Stoye.
\newblock Consensus molecular models for the amino terminal domain of the
  retrovirus restriction gene {\em fv1} and the murine leukaemia virus capsid
  proteins.
\newblock {\em JMC Struc. Biology}, 4:1--15, 2004.

\bibitem{BakerDet05}
D.~Baker and W.~R. Taylor.
\newblock {\em Ab initio} structure prediction.
\newblock In S.~Subramanian, editor, {\em Encyclopedia of genetics, genomics,
  proteonomics and bioinformatics}, volume 7--bioinformatics, pages 3245--3251.
  John Wiley and Sons Ltd., Chichester, U.K., 2005.

\bibitem{LinKet05}
K.~Lin, V.~A. Simossis, W.~R. Taylor, and J.~Heringa.
\newblock A simple and fast secondary structure prediction method using hidden
  neural networks.
\newblock {\em Bioinformatics}, 21:152--159, 2005.

\bibitem{TaylorWRet05}
W.~R. Taylor and A.~Asz\'odi.
\newblock {\em Protein Geometry, Classification, Topology and Symmetry}.
\newblock Institute of Physics, 2005.
\newblock Currently published by CRC Press.

\bibitem{TaylorWR05a}
W.~R. Taylor.
\newblock Stirring the primordial soup.
\newblock {\em Nature}, 434:705, 2005.

\bibitem{TaylorWR05b}
W.~R. Taylor.
\newblock Modelling molecular stability in the {RNA} world.
\newblock {\em J. Compu. Biol. Chem.}, 29:259--272, 2005.

\bibitem{TaylorWR05c}
W.~R. Taylor.
\newblock Protein folds, knots and tangles.
\newblock In J.~Calvo, K.~Millett, E.~Rawdon, and A.~Stasiak, editors, {\em
  Physical and Numerical Models in Knot Theory}, Series on Knots and Everything
  --- Vol. 36, chapter~10, pages 171--202. World Scientific, Singapore, 2005.
\newblock ISBN: 981-256-187-0.

\bibitem{TaylorWR05d}
W.~R. Taylor.
\newblock Protein structure analysis and prediction.
\newblock In S.~Subramanian, editor, {\em Encyclopedia of genetics, genomics,
  proteonomics and bioinformatics}, volume 7--bioinformatics, pages 3245--3251.
  John Wiley and Sons Ltd., Chichester, U.K., 2005.
\newblock Introductory review to section 6 (ed.: W.R.Taylor).

\bibitem{SnellEAet06}
E.~A. Snell, N.~M. Brooke, W.~R. Taylor, D.~Casane, H.~Philippe, and P.~W.~H.
  Holland.
\newblock An unusual choanoflagellate protein released by hedgehog
  autocatalytic processing.
\newblock {\em Proc. Roy. Soc. (B)}, 273:401--407, 2006.
\newblock DOI: 10.1098/rspb.2005.3263.

\bibitem{VesterstromJet06}
J.~Vesterstr{\/o}m and W.~R. Taylor.
\newblock Flexible secondary structure based protein structure comparison
  applied to the detection of circular permutation.
\newblock {\em J. Compu. Biol.}, 13:43--62, 2006.

\bibitem{JonassenIet06}
I.~Jonassen, D.~Klose, and W.~R. Taylor.
\newblock Protein model refinement using structural fragment tessellation.
\newblock {\em Comp. Chem. Bioinformatics}, 30:360--366, 2006.

\bibitem{TaylorWR06a}
W.~R. Taylor.
\newblock Decoy models for protein structure score normalisation.
\newblock {\em J. Molec. Biol.}, 357:676--699, 2006.

\bibitem{TaylorWRet06a}
W.~R. Taylor, K.~Lin, D.~Klose, F.~Fraternali, and I.~Jonassen.
\newblock Dynamic domain threading.
\newblock {\em Proteins, Struct. Funct. Bioinfo.}, 64:601--614, 2006.

\bibitem{TaylorWR06b}
W.~R. Taylor.
\newblock Transcription and translation in an {RNA} world.
\newblock {\em Phil. Trans. R. Soc. {B}}, 361:1751--1760, 2006.

\bibitem{TaylorWR06c}
W.~R. Taylor.
\newblock A molecular model for the origin of protein translation in an {RNA}
  world.
\newblock {\em J. Theor. Biol.}, 243:393--406, 2006.

\bibitem{TaylorWR06d}
W.~R. Taylor.
\newblock Topological accessibility shows a distinct asymmetry in the folds of
  $\beta\alpha$ proteins.
\newblock {\em FEBS Lett.}, 580:5263--5267, 2006.

\bibitem{KloseDet07}
D.~Klose and W.~R. Taylor.
\newblock Protein structure prediction.
\newblock In D.~J.~Balding et~al., editor, {\em Handbook of Statistical
  genetics}, chapter~10, pages 327--344. John Wiley and Sons Ltd., 2007.
\newblock Second edition.

\bibitem{TaylorWR07a}
W.~R. Taylor.
\newblock Protein knots and fold complexity: some new twists.
\newblock {\em Comp. Biol. Chem.}, 31:151--162, 2007.
\newblock doi:10.1016/j.compbiolchem.2007.03.002.

\bibitem{TaylorWR07b}
W.~R. Taylor.
\newblock Evolutionary transitions in protein fold space.
\newblock {\em Curr. Opin. Str. Biol.}, 17:354--361, 2007.

\bibitem{BartlettGJet08}
G.~J. Bartlett and W.~R. Taylor.
\newblock Using scores derived from statistical coupling analysis to
  distinguish correct and incorrect folds in {\em de-novo} protein structure
  prediction.
\newblock {\em Proteins: struct. funct. bioinfo.}, 71:950--959, 2008.

\bibitem{ChelliahVet08}
V.~Chelliah and W.~R. Taylor.
\newblock Functional site prediction selects correct protein models.
\newblock {\em BMC Bioinormatics funct. bioinfo.}, 9(Suppl.1):S13, 2008.

\bibitem{HollupSMet08}
S.~M. Hollup, W.~R. Taylor, and I.~Jonassen.
\newblock Structural fragments in protein model refinement.
\newblock {\em Prot. Peptide Lett.}, 15:964--71, 2008.

\bibitem{TaylorWRet08a}
W.~R. Taylor, G.~J. Bartlett, V.~Chelliah, D.~Klose, K.~Lin, T.~Sheldon, and
  I.~Jonassen.
\newblock Prediction of protein structure from ideal forms.
\newblock {\em Proteins: struct., funct., bioinfo.}, 70:1610--1619, 2008.

\bibitem{MargueronRet09}
R.~Margueron, N.~Justin, K.~Ohno, M.~L. Sharpe, J.~Son, W.~J. Drury~III,
  P.~Voigt, S.~R. Martin, W.~R. Taylor, V.~De~Marco, V.~Pirrotta, D~Reinberg,
  and S.~J. Gamblin.
\newblock Role of the polycomb protein {EED} in the propagation of repressive
  histone marks.
\newblock {\em Nature}, 461:762--767, 2009.

\bibitem{MortuzaGBet09}
G.~B. Mortuza, D.~C. Goldstone, C.~Pashley, L.~F. Haire, M.~Palmarini, W.~R.
  Taylor, J.~P Stoye, and I.~A Taylor.
\newblock Structure of the capsid amino terminal domain from the
  betaretrovirus, {J}aagsiekte sheep retrovirus.
\newblock {\em J. Molec. Biol.}, 386:1179--1192, 2009.

\bibitem{TaylorWRet09a}
W.~R. Taylor, V.~Chelliah, S.~M. Hollup, J.~T. MacDonald, and I.~Jonassen.
\newblock Probing the ``dark matter'' of protein fold-space.
\newblock {\em Structure}, 17:1244--1252, 2009.

\bibitem{MacDonaldJTet10}
J.~T. MacDonald, K.~Maksimiak, M.~I. Sadowski, and W.~R. Taylor.
\newblock {\em De novo} backbone scaffolds for protein design.
\newblock {\em Prot. Struct. Funct. Bioinf.}, 78:1311--1325, 2010.

\bibitem{GraingerBet10}
B~Grainger, M.~I. Sadowski, and W.~R. Taylor.
\newblock Re-evaluating the 'rules' of protein topology.
\newblock {\em J. Compu. Biol.}, 17:1253--1266, 2010.

\bibitem{GoldstoneDCet10}
D.~C. Goldstone, M.~W. Yap, L.~E. Robertson, L.~F. Haire, W.~R. Taylor,
  A.~Katzourakis, J.~P Stoye, and I.~A. Taylor.
\newblock Structural and functional analysis of prehistoric lentiviruses
  uncovers an ancient molecular interface.
\newblock {\em Cell Host Microbe}, 8:248--259, 2010.

\bibitem{TaylorWRet10a}
W.~R. Taylor and Z.~Katsimitsoulia.
\newblock A soft collision detection algorithm for simple {B}rownian dynamics.
\newblock {\em Compu. Biol. Chem}, 34:1--10, 2010.
\newblock {\tt doi.10.1016/jcompbiolchem.2009.11.003}.

\bibitem{KatsimitsouliaZet10a}
Z.~Katsimitsoulia and W.~R. Taylor.
\newblock A hierarchic algorithm for simple {B}rownian dynamics.
\newblock {\em Compu. Biol. Chem}, 34:71--79, 2010.
\newblock {\tt doi.10.1016/j.compbiolchem.2010.01.001}.

\bibitem{SadowskiMIet10a}
M.~I. Sadowski and W.~R. Taylor.
\newblock Protein structures, folds and fold spaces.
\newblock {\em J. Phys.-Condensed Matter}, 22:033103, 2010.

\bibitem{TaylorWRet10b}
W.~R. Taylor and Z.~Katsimitsoulia.
\newblock A coarse-grained model for actin myosin simulation.
\newblock {\em J. Molec. Graph. Model.}, 29:266--279, 2010.

\bibitem{SadowskiMIet10b}
M.~I. Sadowski and W.~R. Taylor.
\newblock On the evolutionary origins of 'fold space continuity': A study of
  topological convergence and divergence in mixed alpha-beta domains.
\newblock {\em J. Struct. Biol.}, 172:244--252, 2010.

\bibitem{DekkerCet11}
C.~Dekker, K.~R. Willison, and W.~R. Taylor.
\newblock On the evolutionary origin of the chaperonins.
\newblock {\em Proteins}, 79:1172--1192, 2011.

\bibitem{FarrowREet11}
R.~E. Farrow, J.~Green, Z.~Katsimitsoulia, W.~R. Taylor, A.~A. Holder, and
  J.~E. Molloy.
\newblock The mechanism of erythrocyte invasion by the malarial parasite, {\em
  {p}lasmodium falciparum}.
\newblock {\em Semin. Cell Dev. Biol.}, 22:953--960, 2011.

\bibitem{HollupSMet11}
S.~M. Hollup, M.~I. Sadowski, I.~Jonassen, and W.~R. Taylor.
\newblock Exploring the limits of fold discrimination by structural alignment:
  A large scale benchmark using decoys of known fold.
\newblock {\em Compu. Biol. Chem.}, 35:174--188, 2011.

\bibitem{SadowskiMIet11a}
M.~I. Sadowski, K.~Maksimiak, and W.~R. Taylor.
\newblock Direct correlation analysis improves fold recognition.
\newblock {\em Compu. Biol. Chem.}, 35:323--332, 2011.

\bibitem{HollupSMet11a}
S.~M. Hollup, E.~Fuglebakk, W.~R. Taylor, and N.~Reuter.
\newblock Exploring the factors determining the dynamics of different protein
  folds.
\newblock {\em Prot. Sci.}, 20:197--209, 2011.

\bibitem{TaylorWRet11a}
W.~R. Taylor, Z.~Katsimitsoulia, and A.~Poliakov.
\newblock Simulation of cell movement and interaction.
\newblock {\em J. Bioinfo. Compu. Biol.}, 9:91--110, 2011.

\bibitem{SadowskiMIet11b}
M.~I. Sadowski and W.~R. Taylor.
\newblock Evolutionary inaccuracy of pairwise structural alignments.
\newblock {\em Bioinformatics}, 2012.
\newblock Epub ahead of print.

\bibitem{HollupSMet11b}
S.~M. Hollup, M.~I. Sadowski, I.~Jonassen, and W.~R. Taylor.
\newblock Exploring the limits of fold discrimination by structural alignment:
  A large scale benchmark using decoys of known fold.
\newblock {\em Compu. Biol. Chem.}, 35:174--188, 2011.

\bibitem{TaylorWRet11b}
W.~R. Taylor and M.~I. Sadowski.
\newblock Structural constraints on the covariance matrix derived from multiple
  aligned protein sequences.
\newblock {\em {PLoS-ONE}}, 6:e28265, 2011.

\bibitem{TaylorWRet12a}
W.~R. Taylor, D.~T. Jones, and M.~I. Sadowski.
\newblock Protein topology from predicted residue contacts.
\newblock {\em Prot. Sci.}, pages 299--305, 2012.

\end{thebibliography}
